---
title: "simpleRegress"
author: "Steven Garcia"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## make a regression model for AGE.



## Model LENGTH ~ AGE  this is an example  

```{r}
AGEmodel <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(AGEmodel)
summary.lm(AGEmodel)
```

## make a regression model for HEADLEN.



## Model LENGTH ~ HEADLEN  this is an example  

```{r}
HEADLENmodel <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(HEADLENmodel)
summary.lm(HEADLENmodel)
```

## make a regression model for HEADWTH.



## Model LENGTH ~ HEADWTH  this is an example  

```{r}
HEADWTHmodel <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(HEADWTHmodel)
summary.lm(HEADWTHmodel)
```

## make a regression model for CHEST.



## Model LENGTH ~ CHEST  this is an example  

```{r}
CHESTmodel <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(CHESTmodel)
summary.lm(CHESTmodel)
```

## make a regression model for AGE.



## Model LENGTH ~ WEIGHT  this is an example  

```{r}
WEIGHTmodel <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(WEIGHTmodel)
summary.lm(WEIGHTmodel)
```

In conclusion, the highest Adjusted R-squared:  0.8434 was Head Length, compared to all the other variables. Among all the models that fit and thus was the best of those was the Head Length.  